---
title: "Assignment on Simulation Lab (Stat-3108)"
output: html_notebook
---

---

### 1. Create a function your `name` to calculate mean, variance, and standard deviation.

```{r}

maruf <- function(nums) {
  mean <- mean(nums)
  varience <- var(nums)
  stdv <- sd(nums)
  return(c(Mean=mean, Varience=varience, SD=stdv))
}

maruf(1:300)

```

---

### 2. Create a function `correl` to calculate correlation coefficient between X and Y. You may generate X and Y from any distribution. Also create a function `RC` to calculate regression coefficient of `Y on X` and `X on Y`.

```{r}

correl <- function(X, Y) {
  res <- cor(X, Y)
  return(c('Correlation Coefficient'= res))
}

RC <- function(formula, data) {
  rel <- lm(formula=formula, data=data)
  return(rel)
}

set.seed(1)

X=c(rnorm(10, 1, 30))
Y=c(rnorm(10, 100, 1000))

data <- data.frame(x=X, y=Y)

RC(y~x, data=data)
RC(x~y, data=data)

```

---

### 3.  Starting with `X0 = 1`, write down the entire cycle for `Xi = 11Xi-1mod (16)`.

```{r}

X <- c(1)

a <- 11
m <- 16
n <- 15

for (i in 1:n){
  X[i+1] <- (a*X[i])%%m
  # 11 <- (11*1)mod(16)
}

R <- X/m
X
R

```

---


### 4.  Implement the pseudo-random number generator: `Xi = 168Xi-1 mod (2^31-1)`. Using the seed `X0 = 123`, run the generator for `10` observations. 

```{r}

X <- c(123)
a <- 168
m <- (2^31)-1
n <- 10
c <- 1
for (i in 1:n){
  X[i+1] <- (a*X[i]+c)%%m
}
X
R<-X/m
R

```

---


### 5.  Implement, test, and compare different methods to generate from a` N (0, 1)` distribution. Generate random samples using the `Box-Müller` algorithm. Create a function normrandbm that:

#### i)  Takes no input variables. 
#### ii) Generates two uniform random numbers `V1, V2~U (0, 1)`
#### iii) Returns two output variables: `X=(-lnV1)^1/2 cos(-2piV2)` and `Y=(-2lnV1)^1/2 sin(2piV2)` .As in a), create a function `bmstats` that can produce? Samples using `normrandbm` and return their `mean`, `median` and `standard deviation`.


```{r}

normrandbm <- function(){
  U1 <- runif(1,0,1)
  U2 <- runif(1,0,1)
  X <- ((-2*log(U1))^(0.5))*cos(2*pi*U2)
  Y <- ((-2*log(U1))^(0.5))*sin(2*pi*U2)
  variables <- c("X" = X,"Y" = Y)
  return(variables)
}


bmstats <- function(n){
  df <- data.frame()
  for(i in 1:n){
    newSample <- normrandbm()
    df[i,1] <- as.numeric(newSample[1])
    df[i,2] <- as.numeric(newSample[2])
  }
  names(df) <- c("X", "Y")
  return(c("Mean(X)"=mean(df$X),
           "SD(X)"=sd(df$X),
           "Mean(Y)"=mean(df$Y),
           "SD(Y)"=sd(df$Y)))
}

bmstats(2300)

```

---


### 6. Generate random samples using inverse-transform method from the following pdf- 
#### `(a) f(x)=10e^-10x; x>0` and `(b) f(x)=1/10(e^-x/10); x>0`

For `a` the CDF is `1-e^-10x`, so `x = -(1/10*log(1-U))`

```{r}

n <- 10
U <- runif(n)
X <- -log(1-U)/10
X
```

For `b` the CDF is `1-e^-1/10x`, so `x = -(10*log(1-U))`

```{r}

n <- 10
U <- runif(n)
X <- -log(1-U)*10
X

```

---


### 8. Let us consider the a discrete random variable `x` follows the following distribution: 

#### `0        1      2        3`
#### `1/8     3/8     3/8     1/8`

### Simulate `100` random samples from the above distribution using `inverse-transformation` methods. Also plot both the `true probability vector` and the `empirical proportions` from simulation and `compare` it.


```{r}

discrete.inv.transform.sample <- function(probabilityVector) {
   U <- runif(1)
   if(U <= probabilityVector[1]){
    return(1)
   }
   for( i in 2:length(probabilityVector)) {
     if(sum(probabilityVector[1:(i-1)]) < U && U <= sum(probabilityVector[1:i])) {
      return(i)
     }
   }
}

num.samples <- 100
probabilityVector<- c(1/8, 3/8, 3/8, 3/8)
names(probabilityVector) <- 0:3
samples <- numeric(num.samples)

for(i in seq_len(num.samples) ) {
 samples[i] <- discrete.inv.transform.sample(probabilityVector)
}

par(mfrow=c(1,2))

barplot(probabilityVector, main='True Probability Mass Function')
barplot(table(samples), main='Empirical Probability Mass Function')

```





