---
title: "Assignment on Simulation Lab (Stat-3108)"
output: html_notebook
---

---

### 1. Create a function your `name` to calculate mean, variance, and standard deviation.

```{r}

maruf <- function(nums) {
  mean <- mean(nums)
  varience <- var(nums)
  stdv <- sd(nums)
  return(c(Mean=mean, Varience=varience, SD=stdv))
}

maruf(1:300)

```
First, we have created a function named `maruf` where it takes one argument `nums`. It can be a range of numbers like `1:300` or `[1, 2, 3, 4, 5]` etc.

---

### 2. Create a function `correl` to calculate correlation coefficient between X and Y. You may generate X and Y from any distribution. Also create a function `RC` to calculate regression coefficient of `Y on X` and `X on Y`.

```{r}

correl <- function(X, Y) {
  res <- cor(X, Y)
  return(c('Correlation Coefficient'= res))
}

RC <- function(formula, data) {
  rel <- lm(formula=formula, data=data)
  return(rel)
}

set.seed(1)

X=c(rnorm(10, 1, 30))
Y=c(rnorm(10, 100, 1000))

data <- data.frame(X, Y)

RC(y~x, data=data)
RC(x~y, data=data)

```


### 3.  Starting with X0 = 1, write down the entire cycle for Xi = 11Xi-1mod (16).

```{r}

X <- c(1)

a <- 11
m <- 16
n <- 15

for (i in 1:n){
  X[i+1] <- (a*X[i])%%m
  # 11 <- (11*1)mod(16)
}

R <- X/m
X

```




### 4.  Implement the pseudo-random number generator: `Xi = 168Xi-1 mod (231-1)`. Using the seed `X0 = 123`, run the generator for `10` observations. 

```{r}

X <- c(123)
a <- 168
m <- (2^31)-1
n <- 10
c <- 1
for (i in 1:n){
  X[i+1] <- (a*X[i]+c)%%m
}
X
R<-X/m
R

```


### Implement the pseudo-random number generator: Xi = 16807Xi-1 mod (231-1). Using the seed X0 = 1234567, run the generator for 100,000 observations. Perform a chi-square goodness-of-fit test on the resulting PRN’s. Use 20 equal-probability intervals and level α = 0.05. Now perform a runs up-anddown test with α = 0.05 on the observations to see if they are independent.

```{r}
X<-c(1234567)
a<-16807
c<-1
m<-(2^31)-1
n<-10000
for (i in 1:n){
X[i+1] <- (a*X[i]+c)%%m
}

R<-X/m

##To perform Chi-Square Test
chisq.test(R)

##Creating a interval
intervals <- seq(0,1,by=0.05)
O <- rep(0,20)
for (i in 1:length(R)){
for (j in 1:20){
if(intervals[j] < R[i] && R[i] <= intervals[j+1]){
O[j] <- O[j] + 1
}
}
}
O
library(lawstat)
runs.test(R)
```













