---
title: "Assignment on Simulation Lab (Stat-3108)"
output: html_notebook
---

---

### 1. Create a function your `name` to calculate mean, variance, and standard deviation.

```{r}

maruf <- function(nums) {
  mean <- mean(nums)
  varience <- var(nums)
  stdv <- sd(nums)
  return(c(Mean=mean, Varience=varience, SD=stdv))
}

maruf(1:300)

```
First, we have created a function named `maruf` where it takes one argument `nums`. It can be a range of numbers like `1:300` or `[1, 2, 3, 4, 5]` etc.

---

### 2. Create a function `correl` to calculate correlation coefficient between X and Y. You may generate X and Y from any distribution. Also create a function `RC` to calculate regression coefficient of `Y on X` and `X on Y`.

```{r}

correl <- function(X, Y) {
  res <- cor(X, Y)
  return(c('Correlation Coefficient'= res))
}

RC <- function(formula, data) {
  rel <- lm(formula=formula, data=data)
  return(rel)
}

set.seed(1)

X=c(rnorm(10, 1, 30))
Y=c(rnorm(10, 100, 1000))

data <- data.frame(X, Y)

RC(y~x, data=data)
RC(x~y, data=data)

```























